Expected Dependency Pair Match:\\ Predicting improvements to {HTER} with expected syntactic structure

### 2009-05-09 mtjournal.tex
included section on initial correlations with HTER

>>>>

\section{Correlations with HTER}

  Corpus
    Gale translation corpus 2.5; 3 sites, 2 source languages, 4 genres each

  prediction:
    Mean-subtracted HTER per-document

  base measure EDPM: F[1g,2g,dl,lh],n=50,gamma=0.25

  [EXPT]
\begin{verbatim}
            Ar     Zh    All
   TER     0.51   0.32  0.44
   BLEU_4 -0.42  -0.33 -0.37
   EDPM   -0.60* -0.39 -0.50*
\end{verbatim}
  point: base EDPM does better on all docs, and on Arabic. difference
  is not quite significant at the p=0.05 on the Chinese documents

  Note 1: also tried pairwise deltas per-document, with similar
  results, as presented in the MetricsMATR competition submission.

  Note 2: when using per-segment mean-subtracted, r values are smaller
  and *Arabic* was the language where EDPM did not perform best.

\begin{verbatim}
               Ar     Zh     All
      TER     0.38*  0.04   0.19
      BLEU_4 -0.10  -0.16  -0.14
      EDPM   -0.31  -0.19* -0.24*
\end{verbatim}

  (Go into details of per-genre differences here? or leave out, for
  space reasons?)
